---
title: "Plotl_ly  وظائف عمل"
author: "Ahmed Alluqmani"
date: 2020-12-01T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

 
 
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```
 
 
# plot_ly()


```{r}

library(plotly)

fig <- plot_ly()

fig

 
```


## plot_ly(r,theta)

```{r plot_ly(r,theta}

library(plotly)
fig <- plot_ly(
 r = c(0,1,2,3),
theta = c(0,45,90,135)
               )

fig


```
 

**APPENDIX plot_Ly(r,theta)**
- plot_ly(r)

```{r plot_ly(r)}
 
library(plotly)
 
fig <- plot_ly(
 r = c(0,1,2,3))

fig


```



- plot_ly(theta)


##  plot_ly(type,fill,name)


**APPENDIX plot_ly(type,fill,name)**



```{r plot_ly(type,fill,name))}
 
library(plotly)

fig <- plot_ly(
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
  type = 'scatterpolar',
           fill = 'toself',
           name = 'Trail'
)

fig

  
```

    Appendix mode (type,modes, fill,names)
      
        plot_ly(mode = markers)
        plot_ly(r = c(0,1,2,3),theta = c(0,45,90,135))
        plot_ly(type = 'scatterpolar')
        plot_ly(modes(markers), plot_ly(lines), plot_ly(lines+markers)
        plotl_ly(fill = 'toself')
        plotl_ly(name = 'Trail')

 
 ---
 
 
 
- plot_ly(type)


```{r plot_ly(type)}
 
library(plotly)

fig <- plot_ly(type = 'scatterpolar')

fig


```




- plot_ly(fill = toself))

```{r plot_ly(fill)}
 
library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
  mode = 'lines+markers',
  fill = 'toself'
)
fig

```


 


- plot_ly(name)

```{r plot_ly(name)}
 
library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
  mode = 'lines+markers',
  fill = 'toself',
  name = 'Trail'
)

fig

``` 
      
      plot_ly(name ='Trail') is unviewed becuase we need to use layout(showlegend = T, showline = T) 
     
        * fig <-  fig %>% layout(showlegend = T, showline = T)
      

 
 ---



## plot_ly(mode)

 
**APPENDIX plot_ly(mode)**

- plot_ly(mode = markers)


```{r plot_ly(mode(markers)}

library(ggplot2)
library(plotly)
fig <- plot_ly(
   type = 'scatterpolar',
 r = c(0,1,2,3),
theta = c(0,45,90,135),
   mode = 'markers' 
)

fig
```


## plot_ly(marker(list))
  

**APPENDIX plot_ly (marker(list(size,color,symbol)))**
-   plot_ly(marker list(size))
 
```{r plot_ly(marker list(size ))}
 
library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
  mode = 'lines+markers', marker = list(size = 10),
  fill = 'toself'
  )
fig

```

-    plot_ly(marker (list(color,symbol)))
 
```{r plot_ly(marker (list(color,symbol)))}
 

library(plotly)

fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
    mode = 'lines+markers', marker = list(size = 10,color="red", 
                                          symbol = 'square' ),
  fill = 'toself'
)


fig



```

 

-  plot_ly(mode = lines)

```{r  plot_ly(mode (lines)}
 
library(plotly)
fig <- plot_ly(
   type = 'scatterpolar',
   r = c(0,1,2,2),
   theta = c(0,45,90,0),
   mode ='lines'
)

fig


```




## plot_ly (lines(list))
 

**APPENDIX plot_ly(lines(list(color, width)))**

plot_ly(lines (list(color, width)))

```{r plot_ly((marker(list), lines(list)))}

library(plotly)

fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
    mode = 'lines+markers', marker = list(size = 10,color="red", 
                                          symbol = 'square' ),
  lines = list(color="black",width=5),
  fill = 'toself'
)


fig
```

        plot_ly(r = c(0,1,2,3),theta = c(0,45,90,135))
        plot_ly(type = 'scatterpolar')
        plot_ly(modes(lines+markers),fill = 'toself')
        plot_ly(mode = 'lines+markers')
        
       *marker = (list(size= 10)
        marker = (list(symbole = 'square')
        marker = (list(color = '-')
       
       *lines = list(color="black")
        lines = list(width=5)
       
 ---
 





**APPENDIX plot_ly(mode) plot_ly(line(list),marker(list))**

-  plot_ly(mode=lines+markers) plot_ly(line(list),marker(list))
 

```{r plot_ly(mode(lines and markers))}
 
library(plotly)

fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
  mode = 'lines+markers'
)

fig

 

```


