---
title: "add_trace وظائف عمل"
author: "Ahmed Alluqmani"
date: 2020-12-01T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

 
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```
 
  
 
# add_trace

## add_trace(r,theta)

```{r}
library('plotly')
fig <- plot_ly(
  type = 'scatterpolar'
)
  
fig <- fig %>%
  add_trace( r = c(0,1,2,3),
  theta = c(180,225,270,315)
  )
fig

 

```


-   Appendix add_trace(r,theta)


-   add_trace(r)

```{r }
library('plotly')
fig <- plot_ly(
  
)
  
fig <- fig %>%
  add_trace( r = c(0,1,2,3)
  )
fig
 
```


-   add_trace(theta)
 

```{r}
library('plotly')
fig <- plot_ly(
  type = 'scatterpolar'
)
  
fig <- fig %>%
  add_trace( r = c(0,1,2,3),
  theta = c(180,225,270,315)
  )
fig

 

```
 Appendix plot_ly() add_trace(r,theta)


- plot_ly(type, mode) add_trace(r,theta) 

```{r}
 
library('plotly')
fig <- plot_ly(
  type = 'scatterpolar',
  mode ='lines+markers' 
)
  
fig <- fig %>%
  add_trace( r = c(0,1,2,3),
  theta = c(180,225,270,315)
  )
fig 
 
 

```

- plot_ly(fill,type, mode) add_trace(r,theta) 

```{r}
library('plotly')
fig <- plot_ly(
  type = 'scatterpolar',
  mode ='lines+markers',
  fill = 'toself'
)
  
fig <- fig %>%
  add_trace( r = c(0,1,2,3),
  theta = c(180,225,270,315)
  )
fig 
 

```



 
## add_trace(line (list), marker (list))
    

```{r}
 library('plotly')
fig <- plot_ly(
  type = 'scatterpolar',
    mode = 'lines+markers', 
  fill = 'toself')
  
fig <- fig %>%
  add_trace( r = c(0,1,2,3),
  theta = c(180,225,270,315),
  line = list(
    color = "blue"),
  marker = list(
    color = "red")
  )
fig
```


-    Appendix add_trace marker(list)

-   add_trace marker(list (red,size))

```{r}
library('plotly')
fig <- plot_ly(
  type = 'scatterpolar',
    mode = 'lines+markers',
  fill = 'toself')
  
fig <- fig %>%
  add_trace( r = c(0,1,2,3),
  theta = c(180,225,270,315),
  line = list(
    color = "blue"),
  marker = list(
    color = "red",size = 6)
  )
fig  


```


 
-   add_trace marker(list (color,size))


```{r}
library('plotly')
fig <- plot_ly(
  type = 'scatterpolar',
    mode = 'lines+markers', 
  fill = 'toself')
  
fig <- fig %>%
  add_trace( r = c(0,1,2,3),
  theta = c(180,225,270,315),
  line = list(
    color = "blue"),
  marker = list(
    color = "red",size = 6, symbol = 'square')
  )
fig 

```


#   add_trace marker(list (symbol))


```{r}
library('plotly')
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
    mode = 'lines+markers', marker = list(size = 10,color="red"),
  lines = list(size = 10,color="black"),
  fill = 'toself',
  name='Trail'
) 
  
fig <- fig %>%
  add_trace( r = c(0,1,2,3),
  theta = c(180,225,270,315),
  line = list(
    color = "blue"),
  marker = list(
    color = "red",size = 6, symbol = 'square')
  )
fig 
 


```








- radialaxis (list(visible, range, angle,color,nticks ,tickcolor))
  
-   Appendix radialaxis = (list)
  
```{r layout(polar list( radialaxis (list()))}
 

library(plotly)

fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
    mode = 'lines+markers', marker = list(size = 10,color="red", 
                                          symbol = 'square' ),
  lines = list(color="black",width=5),
  fill = 'toself'
)

fig <- fig %>%
  layout(
    polar = list( radialaxis = list(
     
    )))
fig



```


    plot_ly(
    type = 'scatterpolar',
    r = c(0,1,2,3),
    theta = c(0,45,90,135),
    mode = 'lines+markers', marker = list(size = 10,color="red", 
                                          symbol = 'square' ),
    lines = list(color="black",width=5),
    fill = 'toself'
    )
    
  ---



-   radialaxis = list(visible, range)))

```{r layout(polar(list(radialaxis (list(visible,range)))))}
 
 library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
  mode = 'lines+markers', marker = list(size = 10,color="red"),
  lines = list(size = 10,color="black"),
  fill = 'toself'
  
) 
fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,3)
      )
    )
  )

fig

 
```



    radialaxis (list(angle))

 

```{r layout(polar list(radialaxis  list(angle)))}

  library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
  marker = list(size = 10,color="red"),
  lines = list(size = 10,color="black"),
  fill = 'toself'
) 
fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,3),
          angle=90
      )
    )
  )

fig
 

```

 

radialaxis(list(color,nticks ,tickcolor)

```{r layout(polar list(radialaxis  list(color,nticks ,tickcolor))}
 
  library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
   marker = list(size = 10,color="red"),
  lines = list(size = 10,color="black"),
  fill = 'toself'
) 
fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,3),
          angle=90,
        color = 'grey',
        nticks = 4,
        tickcolor =toRGB('blue')
      )
    )
  )

fig
 

```
 
### polar((hole)) 

  polar(list(hole=0.5)) 


```{r layout(polar (list(hole))}
 
  library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
   mode = 'lines+markers', marker = list(size = 10,color="red"),
  lines = list(size = 10,color="black"),
  fill = 'toself'
) 
fig <- fig %>%
  layout(
    polar = list(
      hole=0.5
    )
  )

fig

 
 

```


##  layout(showlegend ,showline )
  -- layout(showlegend = T ,showline = F)
  
```{r layout(showlegend ,showline )}
 
  library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
    mode = 'lines+markers', marker = list(size = 10,color="red"),
  lines = list(size = 10,color="black"),
  fill = 'toself'
) 
fig <- fig %>%
  layout(
    polar = list(
      hole=0.2,
      radialaxis = list(
        visible = T,
        range = c(0,3),
          angle=90,
        color = 'grey',
        nticks = 4,
        tickcolor =toRGB('blue')
      )
    ),
      showlegend = T,
    showline = T
  )

fig
 

```


## layout(title)

  -- layout( title = "Radar Charts in R with Plotly") 


```{r layout(title (scene list()) layout(name)}
 
 
  library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
    mode = 'lines+markers', marker = list(size = 10,color="red"),
  lines = list(size = 10,color="black"),
  fill = 'toself',
  name='Trail'
) 
fig <- fig %>%
  layout(
    polar = list(
      hole=0.2,
      radialaxis = list(
        visible = T,
        range = c(0,3),
          angle=90,
        color = 'grey',
        nticks = 4,
        tickcolor =toRGB('blue')
      )
    ),
      showlegend = T,
    showline = T
  )

fig <- fig %>% layout(
  title = "Radar Charts in R with Plotly",
  scene = list(
  ))

fig
 

```


## layout(scene = list)

  -- layout(scene list( xaxis (list(title) yaxis (list(title ) zaxis (list(title)))))

 

```{r layout(scene list( xaxis ( list(title) yaxis (list(title ) zaxis (list(title))))))}
 
 
  library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
    mode = 'lines+markers', marker = list(size = 10,color="red"),
  lines = list(size = 10,color="black"),
  fill = 'toself',
  name='Trail'
) 
fig <- fig %>%
  layout(
    polar = list(
      hole=0.2,
      radialaxis = list(
        visible = T,
        range = c(0,3),
          angle=90,
        color = 'grey',
        nticks = 4,
        tickcolor =toRGB('blue')
      )
    )
  )

fig <- fig %>% layout( showlegend = T,
    showline = T,
  title = "Radar Charts in R with Plotly",
  scene = list(
    xaxis = list(title = "Cos"),
    yaxis = list(title = "Sin"),
    zaxis = list(title = "Z")
  ))

fig




 
```



```{r layout(scene list()}
 
 
  library(plotly)
fig <- plot_ly(
  type = 'scatterpolar',
  r = c(0,1,2,3),
  theta = c(0,45,90,135),
    mode = 'lines+markers', marker = list(size = 10,color="red"),
  lines = list(size = 10,color="black"),
  fill = 'toself',
  name='Trail'
) 
fig <- fig %>%
  layout(
    polar = list(
      hole=0.2,
      radialaxis = list(
        visible = T,
        range = c(0,3),
          angle=90,
        color = 'grey',
        nticks = 4,
        tickcolor =toRGB('blue')
      )
    )
  )

fig <- fig %>% layout(paper_bgcolor='#5875D5',
                      showlegend = T, 
  title = "Radar Charts in R with Plotly",
  scene = list(
    xaxis = list(title = "Cos"),
    yaxis = list(title = "Sin"),
    zaxis = list(title = "Z")
  ), titlefont = list(
  color = '#ffffff',size=12,family = "Agency FB"),
  font = list(family = 'Agency FB',
              size = 10), 
              margin = 0)
  

fig




 
```



